% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4

\documentclass{llncs}
\usepackage{llncsdoc}

\usepackage{url}

\usepackage{graphicx}
\usepackage{graphics}

\usepackage{pgfplots}
\usepackage[utf8]{inputenc}
\newtheorem{cnj}{Conjecture}

\usepackage{amsmath}
\usepackage[utf8]{inputenc}

%
\begin{document}

\title{Cyber-insurance \& endogenous network formation}

\author{Håvard Råmundal Halse\inst{1}, Jonas Hoemsnes\inst{1} \and Gergely Biczók\inst{2}}

\institute{Dept. of Telematics \\
Norwegian University of Science and Technology \\ \{havahals, jonashoe\}@stud.ntnu.no
\and
Dept. of Telematics \\
Norwegian University of Science and Technology \\ gbiczok@item.ntnu.no}

\maketitle
%

\begin{abstract}
Cyber-insurance is a powerful economic concept that can
help companies in the fight against cybercrime. From the early 80s, several
researchers claimed that cyber-insurance had a bright future, were it
would become a huge economical tool for handling residual cyber-risks.
However, both the European and US cyber-insurance market have failed
to grasp its promising potential. To fully grasp this potential they need
innovative approaches to handle the unique problems of cyber-insurance.
This paper find and characterize network structures with properties that
make them superior as cyber-insurance. And creates several models for
forming these network structures. In every model, new properties that
relate the model to the real-world and real-world insurance products are
added. The results show that insurers can use the insurance premium as
a tool for determining the resulting formation of the network, and if set
to the right level, these superior structures will evolve.
We believe our findings could help the cyber-insurance market evolve, by
giving the insurers a proper tool to better analyze and control formation
of cyber-insurance networks.
\end{abstract}
%
\input{introduction}
\input{graphsPaper}

\section{Modeling Cyber-insurance}
\input{modelingCyberIncurance}

\section{Discussion}

%
\begin{thebibliography}{[MT1]}
%
\bibitem[BO1]{bolot:cyber}
  Bolot, Jean and Lelarge, Marc:
  Cyber insurance as an incentive for Internet security
  Managing information risk and the economics of security
  (2008) 269--290
%
\bibitem[BO2]{bolot:cyber2}
	Lelarge, Mark, and Jean Bolot:
	Economic incentives to increase security in the internet: The case for insurance.
	INFOCOM (2009), IEEE.
%
\bibitem[BO3]{bolot:new}
	Bolot, Jean C and Lelarge, Marc
 	A new perspective on internet security using insurance
 	INFOCOM The 27th Conference on Computer Communications. IEEE
 	(2008) 1948--1956
  %
\bibitem[RA1]{ranjan:cyber}
	Pal, Ranjan and Hui, Pan	
	On Differentiating Cyber-Insurance Contracts A Topological Perspective
  	Internet Management Conference (2013), IEEE.
%
\bibitem[PO1]{ccost}
Ponemon Institute
Second Annual Cost of Cyber Crime Study, Benchmark Study of U.S: Companies
Ponemon Institute (2011)
%
\bibitem[ST1]{evolvingcyber}
  Evolving cyber cover
  \url{http://www.strategic-risk.eu/Journals/2012/02/22/i/j/w/RiskFinancing_Mar12.pdf}
  Accessed: 31/01/2013
  %
\bibitem[GN1]{CFCunder}
	Graeme Newman
	Cyber liability in Europe: What insurers should knowL
	CFC Underwriter \url{http://www.cfcunderwriting.com/media/news-articles/european-cyber.aspx}
 	Accessed: 14/02/2013
  %
  \bibitem[BS1]{bohme2010modeling}
  B{\"o}hme, R. and Schwartz, G.
  Modeling cyber-insurance: Towards a unifying framework
  Proceedings of GameSec (2010)
%
\bibitem[LE1]{lieberman2005evolutionary}
Lieberman, Erez and Hauert, Christoph and Nowak, Martin A
 Evolutionary dynamics on graphs
Nature Publishing Group 433-7023 (2005) 312--316

  
\bibitem[CE1]{clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. {\bfseries 78} (1982) 315--333
%
\bibitem[CE2]{clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris {\bfseries 287} (1978) 1013--1015
%
\bibitem[MT1]{mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. {\bfseries 72} (1988) 28--55
%
\bibitem[Ta1]{tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)
%
\bibitem[Ra1]{rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. {\bfseries 33} (1980) 609--633
\end{thebibliography}
%

\end{document}
